---
title: "covid 19"
author: "Tania Boror"
date: "4/2/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 
### This is contained in a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Question 1 - Is dying independent of sex

$H_0$ COVID 19 deaths in Korea, January - May 2020 are unrelated to sex. 
$H_A$ There is a relation between COVID 19 deaths in Korea, January - May 2020 and sex of the patient. 


Table of patients:
```{r}
kRdata$Sex = as.factor(kRdata$Sex)
kRdata$result = as.factor(kRdata$result)

# cross tabulation, patient state by gender

with(kRdata, table(Sex, result))

```

## We create two bar charts - one based on frequency and the other on percent, use ggplot commands to do this

```{r}
dd2 <- kRdata %>% group_by(result,Sex) %>% summarize(count=n()) %>% mutate(prcnt=count/sum(count))


# the group_by followed by summarize(count=n())

basicC <- ggplot(dd2,aes(x=result,y=count,fill=Sex))
basicC + geom_bar(stat="identity",position="dodge")

#Now for percentage plot

basicCC <- ggplot(dd2,aes(x=result,y=prcnt*100,fill=Sex)) 
basicCC + geom_bar(stat="identity", position = "dodge")
```

  
In the observational study, males were more likely to die than females from COVID 19.

$H_A$ There is a relation between COVID 19 deaths in Korea, January - May 2020 and sex of the patient. 
  
## Numerical results


## Inferential results 




## Conclusions

